\vspace{60pt}\\ \huge \bfseries Skedge \\ \vspace{10pt} \Large Smarter course scheduling for our University

### 2016-04-13 introduction.tex
Slight mods

I am proud to finally, officially introduce the world to \emph{Skedge}, a website I have been developing since December 2013. It began as a weekend project after I spent too much time trying to find interesting elective classes, and it wasn't until I briefly presented it at a RocHack ``Hacker Night'' when I realized the potential it had to help others as well. I never expected the subject of my senior thesis to be something so close to my heart, so I am grateful for such a fun and motivating opportunity to continue work on Skedge, and, selfishly, for the outlet of recognition.

@@

``Course Description / Course Schedule,'' (or \emph{CDCS} for short) is the University's official tool for browsing the University's current course catalog \cite{cdcs}.

The CDCS interface consists of a series of form fields for inputting search queries on the left, and search results on the right side (see Figure \ref{fig:cdcs-index}). Despite ``Course Schedule'' being in its name, CDCS does not offer scheduling functionality. Only course times can viewed, and it is up to the user to keep track of the courses they are considering for their next semester.

@@

Better CDCS \cite{better-cdcs} is a browser extension, available for Firefox, Safari, and Chrome, that offers a solution to the lack of scheduling mentioned above. It works by injecting ``Add Section'' and ``Bookmark Section'' buttons into the existing CDCS interface, and providing a tab on top of the screen that will toggle between the user's schedule and the search results (see Figure \ref{fig:cdcs-better}).

@@

Skedge \cite{skedge} is, in short, CDCS combined with Better CDCS on a single platform (see Figure \ref{fig:sk-index}). Like CDCS, it is lightweight, service-oriented, and doesn't require a login, but unlike CDCS, it doesn't require a separate browser extension.

It matches feature-for-feature with the two tools (search options, information displayed, scheduling and course bookmarks, etc.), and aims to improve upon the work of both of them on several fronts, which will be investigated in this paper in great detail. It is my contention that students, parents, faculty, staff, and administration can all benefit from such improvements.

\vspace{20pt}

>>>>

I am proud to finally, officially introduce the world to \emph{Skedge}, a website I have been developing since December 2013. It began as a weekend project after I spent too much time trying to find interesting elective classes, and it wasn't until I briefly presented it at a RocHack ``Hacker Night'' when I realized the potential it had to help others as well. I never expected the subject of my senior thesis to be something so close to my heart, so I am grateful for such a fun and motivating opportunity to continue work on Skedge, and, selfishly, for an outlet of recognition.

@@

``Course Description / Course Schedule,'' (or \emph{CDCS} for short) is the University's official tool for browsing the course catalog \cite{cdcs}. The CDCS interface consists of fields on the left side for inputting a search, and search results on the right side (see Figure \ref{fig:cdcs-index}). Despite ``Course Schedule'' being in its name, CDCS does not offer scheduling functionality. Course times can only be viewed, and it is up to the user to keep track of courses considered for the next semester.

@@

\emph{Better CDCS} \cite{better-cdcs} is a browser extension, available for Firefox, Safari, and Chrome, that offers a solution to the lack of scheduling mentioned above. It works by injecting ``Add Section'' and ``Bookmark Section'' buttons into the existing CDCS interface, and providing a tab on top of the screen that will toggle between the user's schedule and the search results (see Figure \ref{fig:cdcs-better}).

@@

\emph{Skedge} \cite{skedge} is, in short, CDCS combined with Better CDCS on a single platform (see Figure \ref{fig:sk-index}). Like CDCS, it is lightweight, service-oriented, and doesn't require login, but unlike Better CDCS, it also doesn't require a separate browser extension.

It matches feature-for-feature with the two tools (search options, information displayed, scheduling and bookmarks, etc.), and aims to improve upon the work of both on several fronts, which will be investigated in this paper in great detail. It is my contention that students, parents, faculty, staff, and administration can all benefit from such improvements.

\vspace{30pt}
